\documentclass{article}
\usepackage[utf8]{inputenc}
\setlength{\parindent}{0cm}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
     colorlinks=true,
     linkcolor=blue,
     filecolor=blue,
     citecolor = black,      
     urlcolor=blue,
     }
\title{CSCI1410 Gradescope Guide}
\author{}
\date{Fall 2021}

\begin{document}

\maketitle

You will be submitting your assignments on Gradescope. You will also be receiving your grades and feedback via Gradescope. To ensure fully anonymous grading, please follow the instructions below to create both Anonymous ID and email. Once you have completed the instructions, please fill out this \href{https://forms.gle/qT559KRsZLyHWGBe8}{Google form}. 

\section{If you do not have Anonymous ID and email}: 
\subsection{Creating an Anonymous ID}
Create an anonymous id with this \href {http://www.unit-conversion.info/texttools/random-string-generator/}{Random String Generator}.

\subsection{Creating an Anonymous Email}
You will need to create a new gmail address/account. 

Use the above anonymous ID that you have generated as the username for the email, so that your email address with have the format:

$<$your anonymous ID$>$ @gmail.com.

If the account is already taken, generate a new anonymous ID and repeat the steps above. 

Set up email forwarding to your Brown email. 

\subsection{Gradescope Account Creation}

Sign up as a student on with your anonymous email at \href{https://www.gradescope.com/}{gradescope.com}.
The course entry code for Fall 2021 is \textbf{5V63R2}.
Instead of using your real name, use your anonymous ID.
For your student id, put your cs login.

\section{If you have both an anonymous email and an anonymous ID}
If your anonymous email and anonymous ID don't match, that is ok. Please make sure change your student id to your cs login. You can do this by clicking on the ``account" box in the bottom left.
Then select ``edit account".
Re-enter your password if prompted to do so. Then, you may change your student id. 


\end{document}
